PCA Toolkit

### 2019-11-01 pca-toolkit.Rmd
add method overview
add restricted PCs

@@

@@

## Ancestry matching

Method: Robust Mahalanobis distances by reference population.

```{r}

```

>>>>

## Overview of existing methods

```{r, out.width="98%"}
knitr::include_graphics("figures/method-overview.png")
```

@@

## Computing PCs using a subset of individuals

When restricting British to 10K and Irish to 5K: capturing at least 40 PCs!

```{r, out.width="95%"}
knitr::include_graphics("figures/UKBB-scores-restricted.png")
```

@@
